Equilivest: A Robotic Vest to improve Human Balance Rehabilitation*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2022-08-22 iros.tex
Update with a raw version.  Adding all the references.

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

@@

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

@@

\section*{Acknowledgment}

@@

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

>>>>

\begin{abstract}
Stroke is a devastanting disease that affects bla bla bla.
It has been shown that neurofeedback can help patients to regain lost motor activity and recover functionality.
In this work, we are proposing a device that help patients by augmentation sensory sensation and pinning information to certain patterns in gait.  We are presenting results from surveys to patient's caregivers, patients and medical personal.  We are presenting the experimentation paradigm, and the robotic device that we created to help the patient.
\end{abstract}

@@

\section{Introduction}

The form of validation procedures that is required in clinical settings\cite{Papastylianou.etal2016}.

\section{Materials and Methods}

\subsection{Underlying hypothesis}

\begin{itemize}
\item Controlamos que la posición del IMU no supere un umbral, y si lo hace vibra el motor.
\item Intentamos predecir una situación de caída y generar un alerta antes de que ocurra.
\item Hacemos un pacemaker.  Es decir una estimulación sincrónica asociada a la detección de un podómetro.
\end{itemize}

\subsection{Robotic Device Vest}
How does it work, how is the detection of IMU working
Internet of Robotic Things.
Arduino

\subsection{Experimental Design}
How does it work, how is the detection of IMU working
Internet of Robotic Things.
Arduino

@@

\section*{Results}
\section*{Discussion}
\section*{Conclusion}
\section*{Acknowledgment}

@@

\bibliographystyle{IEEEtran}
\bibliography{iros}

\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.
